MSDS 6372 Project 1 Objective 1

### 2020-02-11 Codebook/MSDS6372.Project.O1.Rmd
Update MSDS6372.Project.O1.Rmd

```{r intuitive model}
#To be built and provided by Reagan, there should include about 4 or so intuitive models and we take the one with the best Adj rsquared
```

>>>>

```{r intuitive model}
#To be built and provided by Reagan, there should include about 4 or so intuitive models and we take the one with the best Adj rsquared

rfit <- lm(price ~ minimum_nights + number_of_reviews + tsquare_distance + neighbourhood + room_type + neighbourhood:room_type, data = nyc4)
summary(rfit)
plot(rfit)

rfitl <- lm(log(price) ~ minimum_nights + number_of_reviews + tsquare_distance + neighbourhood + room_type + neighbourhood:room_type, data = nyc4)
summary(rfitl)
plot(rfitl)

```
